Towards Explainability of Machine Learning Models in Insurance Pricing

### 2020-03-02 manuscript/manuscript.Rmd
quick clarification on permuting a variable
mention ordering of variables in attribution definition

More formally, let $y$ denote the vector of responses, $X$ denote the matrix of
predictor variables, $\widehat{f}$ denote the fitted model, and
$L = \mathcal{L}(\widehat{f}(X), y)$, where $\widehat{f}$ applies to $X$
rowwise, denote the value of the loss function, which is mean squared error
in the case of regression. Now, if $\widetilde{X}^{j}$ denotes the predictor
matrix where the $j$th variable has been permuted, then we can compute the
loss with the permuted dataset as
$L^{-j} = \mathcal{L}(\widehat{f}(\widetilde{X}^{j}), y)$. With this, we define
the  variable importance $VI^{j}$ as $L^{-j} - L$.

@@

Formally, for a fitted model $\widehat{f}$ and a specific instance $x_*$, we
would like to decompose the model prediction $\widehat{f}(x_*)$ into

>>>>

More formally, let $y$ denote the vector of responses, $X$ denote the matrix of
predictor variables, $\widehat{f}$ denote the fitted model, and
$L = \mathcal{L}(\widehat{f}(X), y)$, where $\widehat{f}$ applies to $X$
rowwise, denote the value of the loss function, which is mean squared error
in the case of regression. Now, if $\widetilde{X}^{j}$ denotes the predictor
matrix where the $j$th variable has been permuted, then we can compute the
loss with the permuted dataset as
$L^{-j} = \mathcal{L}(\widehat{f}(\widetilde{X}^{j}), y)$. 
Here, by *permuting* a variable, we mean that we randomly rearrange the values 
in the column of data associated with the variable.
With this, we define
the variable importance $VI^{j}$ as $L^{-j} - L$.

@@

Formally, for a fitted model $\widehat{f}$, a given ordering of the variables
$X^1,\dots,X^p$, where $p$ is the number of predictor variables,
and a specific instance $x_*$, we
would like to decompose the model prediction $\widehat{f}(x_*)$ into
